### 2015-04-26 whoop.tex
various updates

\begin{boogie}
const {:lock} unique lock$0: int;

call mutex_lock(lock$0);
\end{boogie}

@@

\begin{lstlisting}
foo.c: error: potential write-write race:

write by entry point ep1, foo.c:36:2
  shared->resource = 4;

write by entry point ep2, foo.c:52:2
  shared->resource = 5;
\end{lstlisting}

@@

\begin{boogie}
procedure foo$ep1(dev: int);
  ...
  ensures _b$ls$entrypoint1$0
    ==> WATCHED_ACCESS_$M.0 == dev + 4
    ==> lock$0_in_LS_$M.0_$entrypoint1;
  ensures _b$ls$entrypoint1$1
    ==> WATCHED_ACCESS_$M.0 == dev + 8
    ==> lock$0_in_LS_$M.0_$entrypoint1;
  ensures _b$ac$entrypoint1$0
    ==> WATCHED_ACCESS_$M.0 == dev + 4
    ==> !WRITTEN_$M.0_$entrypoint1;
  ensures _b$ac$entrypoint1$1
    ==> WATCHED_ACCESS_$M.0 == dev + 8
    ==> !WRITTEN_$M.0_$entrypoint1;
  ...
\end{boogie}

@@

\begin{boogie}
procedure foo$ep1(dev: int);
  ...
  ensures _b$ls$entrypoint1$0
    ==> lock$0_in_LS_$M.0_$entrypoint1;
  ensures _b$ls$entrypoint1$1
    ==> lock$0_in_LS_$M.0_$entrypoint1;
  ensures _b$ac$entrypoint1$0
    ==> !WRITTEN_$M.0_$entrypoint1;
  ensures _b$ac$entrypoint1$1
    ==> !WRITTEN_$M.0_$entrypoint1;
  ...
\end{boogie}

>>>>

\begin{boogie}
const {:lock} unique lock$0: int;
call mutex_lock(lock$0);
\end{boogie}

@@

\begin{lstlisting}
foo.c: error: potential write-write race:
  write by entry point ep1, foo.c:36:2
    shared->resource = 4;
  write by entry point ep2, foo.c:52:2
    shared->resource = 5;
\end{lstlisting}

@@

\begin{boogie}
procedure foo$ep1(dev: int);
  ensures _b$ls$entrypoint1$0
    ==> WATCHED_ACCESS_$M.0 == dev + 4
    ==> lock$0_in_LS_$M.0_$entrypoint1;
  ensures _b$ls$entrypoint1$1
    ==> WATCHED_ACCESS_$M.0 == dev + 8
    ==> lock$0_in_LS_$M.0_$entrypoint1;
  ensures _b$ac$entrypoint1$0
    ==> WATCHED_ACCESS_$M.0 == dev + 4
    ==> !WRITTEN_$M.0_$entrypoint1;
  ensures _b$ac$entrypoint1$1
    ==> WATCHED_ACCESS_$M.0 == dev + 8
    ==> !WRITTEN_$M.0_$entrypoint1;
  ...
\end{boogie}

@@

\begin{boogie}
procedure foo$ep1(dev: int);
  ensures _b$ls$entrypoint1$0
    ==> lock$0_in_LS_$M.0_$entrypoint1;
  ensures _b$ls$entrypoint1$1
    ==> lock$0_in_LS_$M.0_$entrypoint1;
  ensures _b$ac$entrypoint1$0
    ==> !WRITTEN_$M.0_$entrypoint1;
  ensures _b$ac$entrypoint1$1
    ==> !WRITTEN_$M.0_$entrypoint1;
  ...
\end{boogie}
